---
title: "slope_anlayses_summary"
author: "William Hall"
date: "December 1, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath("../.."))
```

```{r, include=FALSE}
library(tidyverse)
source("R/pvaluer.R")

files_to_read <- 
list(fm_overall = "output/fm_slope_overall.rds",
     fm_by_study = "output/fm_slope_by_study.rds",
     plots_overall = "output/plots_overall.rds",
    plots_by_study = "output/plots_by_study.rds")

dfs_and_plots <- 
map(files_to_read, read_rds)


fms <- dfs_and_plots[1:2] %>% 
  map(filter, gender_id == "female") %>% 
  map_at("fm_overall", mutate, data_id = "overall") %>% 
  map(select, gender_id, mid, data_id, fm_tidy) %>% 
  map(unnest) %>% 
  bind_rows() %>% 
  map_at("p.value", format_pval) %>% as_data_frame %>% 
  map_if(is.numeric, round, 2) %>% as_data_frame()

ss <- 
dfs_and_plots[1:2] %>%  
  map_at("fm_overall", mutate, data_id = "overall") %>% 
  map(select, gender_id, mid, data_id, fm_tidy) %>% 
  map(unnest) %>% 
  bind_rows() %>% 
  filter(term == "sc") %>% 
  map_at("p.value", format_pval) %>% as_data_frame %>% 
  map_if(is.numeric, round, 2) %>% as_data_frame()


```


## Stigma consciousness predicting social identity reactance during conversations with men.

###Overall

```{r, results='asis', echo=FALSE}
fms %>% 
  filter(mid == "male_cp" & data_id == "overall") %>% 
  select(-gender_id, -mid, -data_id) %>% 
  knitr::kable()
```

####Simple slopes


```{r, results='asis', echo=FALSE}
ss %>% 
  filter(mid == "male_cp" & data_id == "overall") %>% 
  select(-mid, -data_id) %>% 
  knitr::kable()
```

### Split by study

```{r, results='asis', echo=FALSE}
fms %>% 
  filter(mid == "male_cp" & data_id != "overall") %>% 
  select(-gender_id, -mid) %>% 
  knitr::kable()

```


####Simple slopes


```{r, results='asis', echo=FALSE}
ss %>% 
  filter(mid == "male_cp" & data_id != "overall") %>% 
  select(-mid) %>% 
  arrange(data_id) %>% 
  knitr::kable()
```

### Plots 

#### Overall

```{r, results='asis', echo=FALSE, warning= FALSE}
dfs_and_plots$plots_overall %>% 
  filter(slope_name == "conv_pos_maleC") %>% 
  .$plots
```


#### By study

##### EES

```{r, results='asis', echo=FALSE, warning= FALSE}
dfs_and_plots$plots_by_study %>% 
  filter(slope_name == "conv_pos_maleC" & data_id == "ees") %>% 
  .$plots
```

##### GSS

```{r, results='asis', echo=FALSE, warning= FALSE}
dfs_and_plots$plots_by_study %>% 
  filter(slope_name == "conv_pos_maleC" & data_id == "gss") %>% 
  .$plots
```

##### HWS

```{r, results='asis', echo=FALSE, warning= FALSE}
dfs_and_plots$plots_by_study %>% 
  filter(slope_name == "conv_pos_maleC" & data_id == "hws") %>% 
  .$plots
```


## Stigma consciousness predicting social identity reactance during conversations with women

###Overall

```{r, results='asis', echo=FALSE}
fms %>% 
  filter(mid == "female_cp" & data_id == "overall") %>% 
  select(-gender_id, -mid, -data_id) %>% 
  knitr::kable()
```

####Simple slopes


```{r, results='asis', echo=FALSE}
ss %>% 
  filter(mid == "female_cp" & data_id == "overall") %>% 
  select(-mid, -data_id) %>% 
  knitr::kable()
```

### Split by study

```{r, results='asis', echo=FALSE}
fms %>% 
  filter(mid == "female_cp" & data_id != "overall") %>% 
  select(-gender_id, -mid) %>% 
  knitr::kable()

```


####Simple slopes


```{r, results='asis', echo=FALSE}
ss %>% 
  filter(mid == "female_cp" & data_id != "overall") %>% 
  select(-mid) %>% 
  arrange(data_id) %>% 
  knitr::kable()
```

### Plots 

#### Overall

```{r, results='asis', echo=FALSE, warning= FALSE}
dfs_and_plots$plots_overall %>% 
  filter(slope_name == "conv_pos_femaleC") %>% 
  .$plots
```


#### By study

##### EES

```{r, results='asis', echo=FALSE, warning= FALSE}
dfs_and_plots$plots_by_study %>% 
  filter(slope_name == "conv_pos_femaleC" & data_id == "ees") %>% 
  .$plots
```

##### GSS

```{r, results='asis', echo=FALSE, warning= FALSE}
dfs_and_plots$plots_by_study %>% 
  filter(slope_name == "conv_pos_femaleC" & data_id == "gss") %>% 
  .$plots
```

##### HWS

```{r, results='asis', echo=FALSE, warning= FALSE}
dfs_and_plots$plots_by_study %>% 
  filter(slope_name == "conv_pos_femaleC" & data_id == "hws") %>% 
  .$plots
```

